full title

### 2020-11-20 paper/pldi21/eval.tex
Revised Section 6

To evaluate the effectiveness of the dynamic shortcut, we performed static
analysis for \inred{269} Lodash 4 tests with and without dynamic shortcut.
Figure~\ref{fig:conc-analysis-time} depicts the box plot chart for their
analysis time and for speed up after applying the dynamic shortcut in a
logarithmic scale.  While the base analysis (no-DS) finished \inred{199} out of
\inred{269} tests within 5 minutes, our tool finished all tests with the dynamic
shortcut (DS).  For \inred{199} tests analyzable by both analyses, the analysis
took \inred{168.4} seconds and \inred{12.2} seconds on average without dynamic
shortcut (no-DS) and with dynamic shortcut (DS), and the dynamic shortcut
accelerates \inred{20.16}\textsf{x} the static analysis on average.  Only for
one test using $\jscode{_.sample}$ (a Lodash 4 library that randomly samples a
value from a given array), the static analysis using dynamic shortcut had
\inred{0.81}\textsf{x} speed of the base analysis because of the frequent use of
dynamic shortcut (\inred{24} times).

Unfortunately, since most of Lodash 4 tests use concrete values instead of
non-deterministic user inputs, they could be analyzed via a few number of
dynamic shortcut.  In fact, among \inred{269} tests, \inred{262} tests analyzed
via a single usage of dynamic shortcut without using abstract semantics.
However, the arguments of library functions might include non-deterministic user
inputs in the real-world JavaScript programs.  Thus, we modified Lodash 4
official tests with abstract values to mimic the use patterns of library
functions.  We randomly selected literals and replace subset of them to their
corresponding typed abstract values.  For example, if we pick a numerical
literal \jscode{42}, we modified it to the abstract numeric value
$\top_{\code{num}}$, which represents the all numerical values.  In the
remaining section, we evaluated our tool based on the randomly abstracted tests
of Lodash 4.

For abstracted tests, the dynamic shortcut successfully accelerates the static
analysis.  Figure~\ref{fig:abs-analysis-time} shows the analysis time for the
abstracted tests in a logarithmic scale.  Among \inred{269} abstracted tests,
the base analysis (no-DS) finished \inred{82} tests within 5 minutes.  On the
other hand, the analysis using dynamic shortcut (DS) finished \inred{219} tests.
For \inred{82} tests analyzable by both analyses, the analyses took
\inred{168.4} seconds and \inred{12.2} seconds on average without dynamic
shortcut (no-DS) and with dynamic shortcut (DS), and the dynamic shortcut
accelerates \inred{20.16}\textsf{x} the static analysis on average.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{img/abs-analysis-ratio}
  \vspace*{-1.5em}
  \caption{Time ratio of the finished analysis with dynamic shortcut for
  \inred{219} Lodash 4 \textit{abstracted} tests.}
  \label{fig:abs-analysis-ratio}
  \vspace*{-1.5em}
\end{figure}

For \inred{219} abstracted tests successfully analyzed with the dynamic
shortcut, communication costs between static and dynamic analysis grew
relatively to the number of dynamic shortcuts.  To communicate with the
dynamic analyzer, the static analysis should dump the current abstract state,
send it to the dynamic analyzer, receive the result from the dynamic analysis,
and apply the given update information to the abstract state.  Thus, the
communication costs will increase dependent on the number of dynamic shortcuts.
Figure~\ref{fig:abs-analysis-ratio} shows the time ratio of dynamic and static
analysis parts with communication costs in total analysis time.  On average, the
dynamic analysis occupied \inred{63.30}\%, communication \inred{9.52}\%, and
static analysis \inred{27.17}\% in total analysis time.  If the dynamic
shortcuts are performed less than 10 times, the ratio of communication in total
analysis time is \inred{9.50\%} on average.  The more dynamic shortcuts
performed, the more communication cost is required.  When the number is
between 41 and 50, the ratio of average communication cost is rised to
\inred{10.65\%} in the total analysis time.

@@

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.48\textwidth}
    \includegraphics[width=\linewidth]{img/precision-fail}
    \vspace*{-1.5em}
    \caption{\# Failed Assertions.}
    \label{fig:precision-fail}
  \end{subfigure}
  \begin{subfigure}[t]{0.48\textwidth}
    \includegraphics[width=\linewidth]{img/precision-branch}
    \vspace*{-1.5em}
    \caption{\# Covered Branches.}
    \label{fig:precision-branch}
  \end{subfigure}
  \vspace*{-1em}
  \caption{The comparison of analysis precision without (no-DS) and with (DS)
  dynamic shortcut for \inred{82} \textit{abstracted} tests analyzable by both
  analyses}
  \label{fig:precision}
  \vspace*{-1.5em}
\end{figure}

@@

To evaluate the precision improvement of dynamic shortcut, we used two different
metrics to measure the precision of the analysis results: 1) the number of false
alarms for assertions in tests and 2) the number of branch covered by analysis.
Figure~\ref{fig:precision} depicts the comparison of analysis precision without
(no-DS) and with (DS) dynamic shortcut using two different metrics.

Lodash 4 official tests check the assertions based on
QUnit\footnote{https://qunitjs.com/}, which is a powerful, easy-to-use
JavaScript testing framework.  Since all assertions in each test are passed in
the concrete execution, any assertion failures during static analysis should be
false alarms.  Although we analyzed \textit{abstracted} Lodash 4 tests, the
number of assertion failures during static anlysis could be a metric of
imprecision of the analysis.  Figure~\ref{fig:precision-fail} shows the number
of assertion failures in each test analyzable by both analysis with and
without dynamic shortcut.  The $x$- and $y$-axis denote the analysis without
(no-DS) and with (DS) dynamic shortcut and each $\times$ mark denotes each test.
The top and bottom dotted lines denote the worst and best precision improvement,
and the middle solid line denotes the average improvement.  Thus, dynamic
shortcut reduces assertion failures to at least \inred{1.00}\textsc{x}, at most
\inred{0.54}\textsc{x}, and \inred{0.92}x on average.

Another metric to measure the precision of static analysis is the number of
branches covered during analysis.  If the static analysis is sound, the more
precise analysis covers the less number of branches.  In the similar way with
the number of assertion failures, Figure~\ref{fig:precision-branch} depicts the
the comparison of the number of branches during static analysis without (no-DS)
and with (DS) dynamic shortcut.  In the view point of the branch coverage,
dynamic shortcut successfully cut down the number of covered branches at least
\inred{0.81}\textsc{x}, at most \inred{0.51}\textsc{x}, and
\inred{0.68}\textsc{x} on average.

\inred{TODO - Case Study.}

@@

Table~\ref{table:func-replace} describes the dynamic shortcut effectively lessen
the burden of manual modeling for JavaScript built-in functions.  Among Lodash 4
\inred{219} abstracted tests analyzable with dynamic shortcut, we measured the
number of tests using only dynamic shortcut instead of manual modeling for each
JavaScript built-in library.  For each raw, \textbf{Object} column denotes the
built-in object, \textbf{Function} function name, \textbf{\# Replaced} the
number of tests successfully replacing the modeling via dynamic shortcut with
the total number of tests using the target function.  For example, the fourth
row in the left side describes that \jscode{Array.prototype.toString} is used in
\inred{139} Lodash 4 abstracted tests and the static analysis with dynamic
shortcut successfully analyze \inred{92} tests among them.  It means that
\inred{66}\% of tests using \jscode{Array.prototype.toString} could be analyzed
without the manual modeling of the built-in function.

Moreover, \inred{6} functions out of \inred{49} JavaScript built-in functions
are analyzed by only dynamic shortcut instead of manual modeling for all Lodash
4 tests.  Each raw colored colored with \inred{yellow} describes such case in
Table~\ref{table:func-replace}.  It means that the manual modeling of \inred{6} 
JavaScript built-in functions is does not required to analyze all Lodash 4
abstracted tests. \inred{TODO - Explain the detail for each case.}

>>>>

To evaluate the effectiveness of the dynamic shortcut, we performed static
analysis for \inred{269} Lodash 4 tests with and without dynamic shortcut.
Figure~\ref{fig:conc-analysis-time} depicts the histogram for their analysis
time and the box plot for speed up after applying the dynamic shortcut.  While
the base analysis (no-DS) finished \inred{199} out of \inred{269} tests within 5
minutes, our tool finished all tests with the dynamic shortcut (DS).  For
\inred{199} tests analyzable by both analyses, the analysis took \inred{168.4}
seconds and \inred{12.2} seconds on average without dynamic shortcut (no-DS) and
with dynamic shortcut (DS), and the dynamic shortcut accelerates
\inred{20.16}\textsf{x} the static analysis on average.  Only for one test using
$\jscode{_.sample}$ (a Lodash 4 library that randomly samples a value from a
given array), the static analysis using dynamic shortcut had
\inred{0.81}\textsf{x} speed of the base analysis because of the frequent use of
dynamic shortcut (\inred{24} times).

Unfortunately, since most of Lodash 4 tests use concrete values instead of
non-deterministic user inputs, they could be analyzed via a few number of
dynamic shortcut.  In fact, among \inred{269} tests, \inred{262} tests analyzed
via a single usage of dynamic shortcut without using abstract semantics.
However, the arguments of library functions might include non-deterministic user
inputs in the real-world JavaScript programs.  Thus, we modified Lodash 4
official tests with abstract values to mimic the use patterns of library
functions.  We randomly selected literals and replace one of them to their
corresponding typed abstract values.  For example, if we pick a numerical
literal \jscode{42}, we modified it to the abstract numeric value
$\top_{\code{num}}$, which represents the all numerical values.  In the
remaining section, we evaluated our tool based on the \textit{original} tests
and the \textit{abstracted} tests of Lodash 4.

Also for abstracted tests, the dynamic shortcut successfully accelerates the
static analysis.  Figure~\ref{fig:abs-analysis-time} shows the analysis time for
the abstracted tests.  Among \inred{269} abstracted tests, the base analysis
(no-DS) finished \inred{82} tests within 5 minutes.  On the other hand, the
analysis using dynamic shortcut (DS) finished \inred{219} tests.  For \inred{82}
tests analyzable by both analyses, the analyses took \inred{168.4} seconds and
\inred{12.2} seconds on average without dynamic shortcut (no-DS) and with
dynamic shortcut (DS), and the dynamic shortcut accelerates
\inred{20.16}\textsf{x} the static analysis on average.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{img/abs-analysis-ratio}
  \vspace*{-1.5em}
  \caption{Analysis time ratio for \inred{219} Lodash 4 \textit{abstracted}
  tests.}
  \label{fig:abs-analysis-ratio}
  \vspace*{-1.5em}
\end{figure}

Unlike Lodash 4 original tests, \inred{xx} dynamic shortcuts are invoked during
analysis for \inred{82} abstracted tests analyzable by both analyses.  We expect
the analysis time with dynamic shortcuts is propositioned to the number of
dynamic shortcuts. To communicate with the dynamic analyzer, the static analysis
should dump the current abstract state, send it to the dynamic analyzer, receive
the result from the dynamic analysis, and apply the given update information to
the abstract state.  Thus, the communication costs might increase dependent on
the number of dynamic shortcuts.  To experimentally evaluate our predictions,
we also evaluated the relationship between the number of dynamic shortcuts and
the communication costs between static and dynamic analysis.  For \inred{xx}
Lodash 4 original tests, the communication cost occupied only \inred{x.xx}\% of
total analysis.  However, for \inred{xx} abstracted tests, the communication
cost occupied \inred{xx.xx}\% in total analysis.
Figure~\ref{fig:abs-analysis-ratio} shows the detailed analysis time ratio for
\inred{82} Lodash 4 original tests.  The $x$-axis denotes the number of dynamic
shortcuts with the number of corresponding tests, and $y$-axis represents the
time ratio normalized by the total analysis time with dynamic shortcuts.  For
all \inred{82} tests, while it shows that the dynamic static analysis occupied
only \inred{x.xx}\% and \inred{27.17}\% in total analysis time, the
communication cost occupied \inred{xx.xx}\%.  If the dynamic shortcuts are
performed less than 10 times, the ratio of communication in total analysis time
is endurable because it occupied only \inred{xx.xx\%} on average.   However,
when \inred{21-30} dynamic shortcuts are performed, the communication occupied
\inred{80\%} of analysis time.  Moreover, the number of dynamic shortcuts is
more than \inred{30}, the communication time itself (DS-Comm.) is over than the
analysis time without dynamic shortcuts (no-DS).  Based on the evaluation, we
believe that it is possible to leverage dynamic shortcuts by optimizing the
communication between static and dynamic analysis.

@@

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.48\textwidth}
    \includegraphics[width=\linewidth]{img/conc-precision}
    \vspace*{-1.5em}
    \caption{Reachable branches for \inred{xx} \textit{original} tests}
    \label{fig:precision-fail}
  \end{subfigure}
  \begin{subfigure}[t]{0.48\textwidth}
    \includegraphics[width=\linewidth]{img/abs-precision}
    \vspace*{-1.5em}
    \caption{Reachable branches for \inred{82} \textit{abstracted} tests}
    \label{fig:precision-branch}
  \end{subfigure}
  \vspace*{-1em}
  \caption{The comparison of analysis precision without (no-DS) and with (DS)
  dynamic shortcut based on the branch coverage of analysis.}
  \label{fig:precision}
  \vspace*{-1.5em}
\end{figure}

@@

To evaluate the precision improvement of dynamic shortcut, we used the number of
branches covered by analysis to measure the precision of the analysis results.
One of the most popular application of static analysis is dead code elimination
by using the result of reachability analysis.  To acquire smaller codes, precise
reachability analysis is required.  Thus, we decided to measure the analysis
precision based on the number of branches covered by analysis.  The high
branch coverage denotes the low analysis precision, and low branch coverage
denotes the high precision.  Figure~\ref{fig:precision} depicts the comparison of
the number of covered branches without (no-DS) and with (DS) dynamic shortcuts
for \inred{xx} original tests and \inred{xx} abstracted tests.

For \inred{xx} both analyzable original tests, Figure~\ref{fig:conc-precision}
shows the number of branches covered by analysis.  The $x$- and $y$-axis denote
the analysis without (no-DS) and with (DS) dynamic shortcuts and each $\times$
mark denotes each test.  The top and bottom dotted lines denote the worst and
best precision improvement, and the middle solid line denotes the average
improvement.  Thus, dynamic shortcuts successfully reduced the number of
branches at least \inred{1.00}\textsc{x}, at most \inred{0.54}\textsc{x}, and
\inred{0.92}x on average.  For abstracted tests, we evaluated \inred{xx} tests
analyzable by both analyses.  Figure~\ref{fig:precision-branch} depicts the
results of experiments for abstracted tests and it shows that dynamic shortcuts
also successfully cuts down the number of covered branches at least
\inred{0.81}\textsc{x}, at most \inred{0.51}\textsc{x}, and
\inred{0.68}\textsc{x} on average.

@@

Table~\ref{table:func-replace} describes the dynamic shortcut effectively lessen
the burden of manual modeling for JavaScript built-in functions.  For Lodash 4
\inred{xx} original tests and \inred{xx} abstracted tests, we measured the
number of tests using only dynamic shortcut instead of manual modeling for each
JavaScript built-in library.  For each raw, \textbf{Object} column denotes the
built-in object, \textbf{Function} function name, \textbf{\# Replaced} the
number of tests successfully replacing the modeling via dynamic shortcut with
the total number of tests using the target function.  For example, the fourth
row in the left side describes that \jscode{Array.prototype.toString} is used in
\inred{139} original tests and \inred{xxx} abstracted tests. Amogn them,
\inred{44} original tests \inred{xx} abstracted tests are successfully analyzed
by dynamic shortcuts instead of using the modeling of
\jscode{Array.prototype.toString}.

Moreover, several built-in functions are analyzed by only dynamic shortcuts in
all tests.  Among \inred{49} JavaScript built-in functions, \inred{xx} and
\inred{xx} functions are analyzed by only dynamic shortcut instead of manual
modeling for all original or all abstracted tests.  Each cell colored by
\inred{yellow} describes fully replaceable cases in
Table~\ref{table:func-replace}.
